Testing Theories of Expectation Formation using Probabilistic Forecasts

### 2019-06-23 paper/Draft.tex
almost finish the theory graphs. Illustrating NI. Different rigidities. IR plots of Pop moms.

@@

Figure \ref{ir_popind} plots the impulse responses of individual and population moments of forecasts accroding to different theories. As we focus on the dynamics of revision as one approaches the terminate date, i.e. forecast of $y_{t+h}$ at $t$, $t+1$, $t+2$ till $t+h$ instead of forecasts with fixed horizon, i.e. $y_{t+h}$,$y_{t+h+1}$.

@@

\begin{figure}[h]\label{ir_popind}
	\centering
	\includegraphics[width=13cm]{figures/ir_indseni.png}
	\includegraphics[width=13cm]{figures/ir_popseni.png} \\
	\caption{Impulse responses of moments to a shock to inflation}
\end{figure}

@@

\begin{table}[]\label{NullTestTable}
	\caption{Test of Rationality and Efficicency}
	\begin{tabular}{lll}

>>>>

Figure \ref{IllustrateNI} illustrates both the signal extraction problem at each period of $t+k$ and how it is used to predict the prediction of $y_{t+h}$.

\begin{figure}[h]\label{IllustrateNI}
	\centering
	\includegraphics[width=13cm]{figures/ni_illustration.png}  
	\caption{Illustration Noisy Information}
\end{figure}

@@

Figure \ref{ir_pop} plots the impulse responses of population moments of forecasts accroding to different theories. As we focus on the dynamics of revision as one approaches the terminate date, i.e. forecast of $y_{t+h}$ at $t$, $t+1$, $t+2$ till $t+h$ instead of forecasts with fixed horizon, i.e. $y_{t+h}$,$y_{t+h+1}$.

@@

\begin{figure}[h]\label{ir_pop}
	\centering
	\includegraphics[width=14cm]{figures/ir_popseni.png} 
	\caption{Impulse responses of moments to a shock to inflation}
\end{figure}

One of the common predictions of SE and NI is there is information rigidity or stickiness of expecatations.  But both theory have suble difference in implied rigidity. I illustrate this in Figure \ref{rigidity}. One notable difference is that SE's rigidty is exogeously fixed. NI's rigidity is endogeously determined by the noisiness of the signals and it is time varying.

\begin{figure}[h]\label{rigidity}
	\centering
	\includegraphics[width=13cm]{figures/rigidity.png} 
	\caption{Rigidity from Two Models}
\end{figure}

@@

\begin{table}[]\label{NullTestTable}
	\caption{Test of Rationality and Efficicency}
	\centering 
	\begin{tabular}{lll}
